
\chapter{Analysis/Methodology}  

\section{Descriptive Statistics/ Text-related statistics}

In this section we generate a set of descriptive/text-related statistics from the query logs. The goal is to perform a comparison of the linguistic and grammatical composition of the query logs, neglecting semantical information of the queries.    
Specifically, we perform a hypothesis test to determine if the syntactical differences between the AQL and the other query logs are statistically significant. For this analysis, we subdivide queries into different syntactical subcategories and measure the frequencies of these subcategories. We consider named entities, words and characters as syntactical subcategories.   
\section{Characteristics-based}
Here, various characteristics of the data sets are measured and displayed. The comparison of these characteristics should provide a first impression of the involved query logs' nature.

\begin{itemize}
    \item Query length 
    \begin{itemize}
        \item Length in words 
        \begin{itemize}
            \item mapping->group->reduction
        \end{itemize} 
        \item Length in characters \begin{itemize}
            \item mapping->group->reduction
        \end{itemize} 
        \item Plot histogram
    \end{itemize}
    \item Unique queries
    \begin{itemize}
        \item Proportion of unique queries group by query
        \item List of top n most common queries
        \begin{itemize}
            \item group->reduction->sort
        \end{itemize} 
        \item Compare most common queries
    \end{itemize}

    \item Token frequency
    \begin{itemize}
        \item Zipf's Law of words and/or queries
        \begin{itemize}
            \item Words:  flat mapping->group->reduction
        \end{itemize}
        \begin{itemize}
            \item Queries: group->reduction
            \item character-based (evtl. anderes gesetz)
            \item total number of characters
        \end{itemize}
        \item Heap's Law
        \begin{itemize}
            \item group->reduction
        \end{itemize} 
    \end{itemize}
    \item Search Operators
    \begin{itemize}
        \item Frequency of operators
        \begin{itemize}
            \item flat mapping->group by
        \end{itemize}
        \item most common operators
        \item phrasensuche, site:
    \end{itemize}
    \item Word frequencies
    \begin{itemize}
        \item most common words, bigrams, n-grams
        \item list of top n common words, bigrams, n-grasms
        \item flat_mapping (apply tokenizer) -> group-by token -> count
        \item total number of words
    \end{itemize}
    \item Word lengths
    \begin{itemize}
        \item can be measured during word-frequency-experiment?
        \item average word length, deviation, distribution of word lengths? 
    \end{itemize}
    
\end{itemize} 



\section{Distribution-based}
In this section, distributions of labels are created from different NLP predictors. The general idea is to compare the different data sets according to their resulting distributions of different domains.  
\begin{itemize}
    \item Plausibilitätsstudie für die classifier: 50-100 samples pro label pro classifier: manuell annotieren und dann accuracy bestimmen.
    \item Intent
    \begin{itemize}
        \item Navigational, transactional and informational
        \begin{itemize}
            \item mapping (apply ORCAS-I classifier)
        \end{itemize}
    \end{itemize}
    \item Named Entities
    \begin{itemize}
        \item Frequency of named entities \begin{itemize}
            \item flat mapping->group->reduction
        \end{itemize} 
        \item Most common named entities
        \item Categorize named entities according to ... -> apply classifier?
    \end{itemize}
    \item Hate speech
    \begin{itemize}
        \item mapping (apply hate speech classifier)
    \end{itemize}
    \item NSFW
    \begin{itemize}
        \item mapping (apply NSFW classifier)
    \end{itemize}
    \item Spam
    \begin{itemize}
        \item mapping (apply spam classifier)
    \end{itemize}
    \item Content
    \begin{itemize}
        
        \item Classify into topic taxonomy 
        \begin{itemize}
            \item mapping apply topic classifier
        \end{itemize}
    \end{itemize}
    
\end{itemize}
\section{Temporal-based}
\begin{itemize}
    \item Discover Google Trends in Data
    \item Plot frequency of selected topics over time per data set
    \item Seasonal topics

    
\end{itemize}
\section{Embedding-based}
\begin{itemize}
    \item Extract document vectors from e.g. BERT
    \begin{itemize}
        \item Create t-SNE plot with regard to intent, topics,... further categories
        \item Apply clusterting algorithm and compare resulting clustersX 
    \end{itemize}
    \item Topic Modeling
        \begin{itemize}
            \item Compare most common topics
            \item Compare variety of topics
        \end{itemize}
\end{itemize}


